---
title: "DATA606lab4a"
author: "jim lung"
date: "03-10-2017"
output: html_document
---

```{r }
load("more/ames.RData")
```


```{r }
area <- ames$Gr.Liv.Area
price <- ames$SalePrice
```

```{r }
summary(area)
```

```{r }
hist(area)
```
Exercise 1

Describe this population distribution.
The population distribution is unimodal and right skewed, the mean is to the right and concentrated on the lower end of the distribution.

```{r }
samp1 <- sample(area, 50)
samp1
```

Exercise 2
Describe the distribution of this sample. How does it compare to the distribution of the population?

The sample distribution is also right skewed and unimodal, the pattern is similar.
```{r }
mean(samp1)
hist(samp1)
```

Exercise 3
Take a second sample, also of size 50, and call it samp2. How does the mean of samp2 compare with the mean of  samp1? Suppose we took two more samples, one of size 100 and one of size 1000. Which would you think would provide a more accurate estimate of the population mean?

```{r }
samp2 <- sample(area, 100)
hist(samp2)
```

```{r }
samp3 <- sample(area, 1000)
hist(samp3)
```
```{r }
mean(samp1)
mean(samp2)
mean(samp3)
```

It is proved more accuate estimate of the population mean by using larger sample size - 1000 than smaller. The sample size is bigger, the sample mean is closer to the population mean.

```{r }
sample_means50 <- rep(NA, 5000)

for(i in 1:5000){
   samp <- sample(area, 50)
   sample_means50[i] <- mean(samp)
   }

hist(sample_means50)
```

```{r }
hist(sample_means50, breaks = 25)
```

Exercise 4
How many elements are there in sample_means50? Describe the sampling distribution, and be sure to specifically note its center. Would you expect the distribution to change if we instead collected 50,000 sample means?


```{r }
length(sample_means50)

```
5000 elements are in sample_mean50.

The distriubtion will be more actuate and similar to the population distribution if the larger sample size of 50000.

```{r }
summary(sample_means50)

```

```{r }
sample_means50 <- rep(NA, 5000)

for(i in 1:5000){
   samp <- sample(area, 50)
   sample_means50[i] <- mean(samp)
   print(i)
   }
```

Exercise 5
To make sure you understand what you¡¦ve done in this loop, try running a smaller version. Initialize a vector of 100 zeros called sample_means_small. Run a loop that takes a sample of size 50 from area and stores the sample mean in sample_means_small, but only iterate from 1 to 100. Print the output to your screen (type  sample_means_small into the console and press enter). How many elements are there in this object called  sample_means_small? What does each element represent?

```{r }
sample_means_small <- rep(NA, 100)

for(i in 1:100){
   samp <- sample(area, 50)
   sample_means_small[i] <- mean(samp)
}
sample_means_small
```

100 elements are in this sample_means_small. It is 100 sample mean collected from 50 sample area.

